|

### 2022-06-14 draft-1.Rmd
Methods Citations

For this analysis, three mental health outcomes were considered: (1) general mental health (Feng & Astell-Burt, 2017; Houlden et al., 2019; Wheeler et al., 2015; Zhang et al., 2017),  (2) depression (Beyer et al., 2014; McEachen et al., 2015), and (3) poor sleep (Shin et al., 2020; Johnson et al., 2018; Feng et al., 2020). General mental health is defined as poor mental health for more than 14 days over the last month, depression is based on reported depression diagnoses from a health professional, and poor sleep is defined as regularly getting less than seven hours of sleep during a 24-hour period (CDC, 2022). The CDC PLACES dataset (CDC, 2022) from 2020 was used for mental health indicators. The PLACES dataset offers model-based, population-level community estimates of health outcomes, both physical and mental (CDC, 2022). All data is for adults aged 18 years or older.

@@

This study identifies greenspace as areas encompassed by the Trust for Public Land’s ParkServe (ParkServe) dataset and The Protected Area Database of the United States (PAD-US) dataset from 2020 (Runkle et al., 2022; Slawsky et al., 2022; TPL 2020; USGS 2020). ParkServe is a dataset comprising all public parks, including local and city parks and playgrounds (TPL 2020). PAD-US is a spatial dataset of all government-managed greenspaces, such as national forest land, national parks, and historical areas (USGS 2020). All parks and public greenspaces selected from these two datasets were combined to form one public greenspace dataset (Figure \@ref(fig:gs-extent)). For consistency with the PLACES mental health datasets at the ZIP Code level, greenspace area was calculated as the percentage of an area within each ZIP code covered by greenspace (defined by the ParkServe and PAD-US datasets); redundant or overlapping greenspaces (i.e., the same greenspace within both datasets) were removed by performing a spatial union of the two datasets, such that overlapping greenspaces do not overestimate greenspace area.

@@

For this analysis, greenspace quality was determined by looking at vegetation health, trail density, and amenity access as three separate quality metrics. Normalized difference vegetation index (NDVI) data (“Landsat-8 Imagery” 2019), ParkServe (TPL, 2020), and OpenStreetMap amenities data (OpenStreetMap, 2022) were used as metrics of greenspace quality. NDVI assesses vegetation density and health, which has been associated with improved mental health outcomes (Wood et al., 2018; Mears et al., 2019). This study calculated NDVI from Landsat-8 imagery from the months of June to August 2019 and filtered images by those with less than ten percent cloud cover. A spatial buffer of 1 km around the greenspace extent was used in calculating the mean NDVI within each greenspace to remove the effects of small “holes” in the dataset and for small parks whose area was smaller than the resolution of Landsat-8 imagery (30 meters).

Greenspace amenities data from ParkServe, specifically trail accessibility, and OpenStreetMap (OSM) data, provided information on how many greenspace-related amenities (e.g., restrooms, parking) are present in each ZIP Code. OSM data was queried for the study area with the _osmdata_ package for R (Padgham 2017) and subsequently spatially filtered to within a 1-km buffer of greenspace extent. This allows for amenities that are “nearby” to greenspaces (e.g., restrooms, restaurants, parking) to factor into greenspace quality. Amenities were summarized as the count of amenities within the 1-km buffer of greenspace extent, and were counted for each ZIP code.

@@

Additional demographic predictor variables include population, race, and household income. Previous research has illustrated that race (Browning & Rigolon, 2018) and income (Hoffiman et al., 2017; deVries et al., 2020) influence the greenspace mental health relationship, as predominantly white, upper-class neighborhoods tend to have the greatest access to greenspaces (Rigolon et al., 2018). Race was accounted for by including the percentage of White residents, and income was accounted for by including the percentage of households with annual income over \$125,000/year. Race and Income variables are from 2018 ACS 5-year estimates (U.S. Census Bureau, 2018).

@@

All variables were tested for spatial autocorrelation; Moran’s I was used to assess spatial autocorrelation at a significance level of $p < 0.05$. *P*-values at or below 0.05 and an Moran’s I-statistic of $I \neq 0$ indicate spatial autocorrelation and spatial dependence, pointing to the need to perform spatial regression (Anselin, 2009; Legendre, 1993). The spatial weights matrix $W_{ij}$ was defined using the queen’s case rule. All variables except population, income and greenspace amenities were found to be spatially autocorrelated (Table \@ref(tab:moran-table)). Variables were tested for multicollinearity, no variables were above the threshold of 5 (Table \@ref(tab:vif)) (Craney & Surles, 2002).

@@

All regression analysis considered greenspace metrics (quantity, NDVI, trail density, and amenities) in addition to percent of the ZIP Code that is White and percent of households in each ZIP Code that makes over \$125,000 per year. All regression analyses were performed in RStudio version 2022.2.3.492 with R version 4.2.0 (2022-04-22 ucrt) (RStudio Team, 2022; R Core Team, 2022).

>>>>

For this analysis, three mental health outcomes were considered: (1) general mental health [@feng2017; @houlden2019; @wheeler2015; @zhang2017],  (2) depression [@beyer2014; @mceachan2016], and (3) poor sleep [@shin2020; @johnson2018; @feng2020]. General mental health is defined as poor mental health for more than 14 days over the last month, depression is based on reported depression diagnoses from a health professional, and poor sleep is defined as regularly getting less than seven hours of sleep during a 24-hour period [@cdc2022]. The CDC PLACES dataset [@cdc2022] from 2020 was used for mental health indicators. The PLACES dataset offers model-based, population-level community estimates of health outcomes, both physical and mental [@cdc2022. All data is for adults aged 18 years or older.

@@

This study identifies greenspace as areas encompassed by the Trust for Public Land’s ParkServe (ParkServe) dataset and The Protected Area Database of the United States (PAD-US) dataset from 2020 [@runkle2022; @slawsky2022; @tpl2021; @prior-magee2020]. ParkServe is a dataset comprising all public parks, including local and city parks and playgrounds [@tpl2021]. PAD-US is a spatial dataset of all government-managed greenspaces, such as national forest land, national parks, and historical areas [@prior-magee2020]. All parks and public greenspaces selected from these two datasets were combined to form one public greenspace dataset (Figure \@ref(fig:gs-extent)). For consistency with the PLACES mental health datasets at the ZIP Code level, greenspace area was calculated as the percentage of an area within each ZIP code covered by greenspace (defined by the ParkServe and PAD-US datasets); redundant or overlapping greenspaces (i.e., the same greenspace within both datasets) were removed by performing a spatial union of the two datasets, such that overlapping greenspaces do not overestimate greenspace area.

@@

For this analysis, greenspace quality was determined by looking at vegetation health, trail density, and amenity access as three separate quality metrics. Normalized difference vegetation index (NDVI) data [@landsat2019], ParkServe [@tpl2021], and OpenStreetMap amenities data [@openstreetmap2022] were used as metrics of greenspace quality. NDVI assesses vegetation density and health, which has been associated with improved mental health outcomes [@wood2018; @mears2019]. This study calculated NDVI from Landsat-8 imagery from the months of June to August 2019 and filtered images by those with less than ten percent cloud cover. A spatial buffer of 1 km around the greenspace extent was used in calculating the mean NDVI within each greenspace to remove the effects of small “holes” in the dataset and for small parks whose area was smaller than the resolution of Landsat-8 imagery (30 meters).

Greenspace amenities data from ParkServe, specifically trail accessibility, and OpenStreetMap (OSM) data, provided information on how many greenspace-related amenities (e.g., restrooms, parking) are present in each ZIP Code. OSM data was queried for the study area with the _osmdata_ package for R [@padgham2017] and subsequently spatially filtered to within a 1-km buffer of greenspace extent. This allows for amenities that are “nearby” to greenspaces (e.g., restrooms, restaurants, parking) to factor into greenspace quality. Amenities were summarized as the count of amenities within the 1-km buffer of greenspace extent, and were counted for each ZIP code.

@@

Additional demographic predictor variables include population, race, and household income. Previous research has illustrated that race [@browning2018] and income [@hoffimann2017; @devries2020] influence the greenspace mental health relationship, as predominantly white, upper-class neighborhoods tend to have the greatest access to greenspaces [@rigolon2018]. Race was accounted for by including the percentage of White residents, and income was accounted for by including the percentage of households with annual income over \$125,000/year. Race and Income variables are from 2018 ACS 5-year estimates [@uscensus2018].

@@

All variables were tested for spatial autocorrelation; Moran’s I was used to assess spatial autocorrelation at a significance level of $p < 0.05$. *P*-values at or below 0.05 and an Moran’s I-statistic of $I \neq 0$ indicate spatial autocorrelation and spatial dependence, pointing to the need to perform spatial regression [@anselin2008; @legendre1993]. The spatial weights matrix $W_{ij}$ was defined using the queen’s case rule. All variables except population, income and greenspace amenities were found to be spatially autocorrelated (Table \@ref(tab:moran-table)). Variables were tested for multicollinearity, no variables were above the threshold of 5 (Table \@ref(tab:vif)) [@craney2002].

@@

All regression analysis considered greenspace metrics (quantity, NDVI, trail density, and amenities) in addition to percent of the ZIP Code that is White and percent of households in each ZIP Code that makes over \$125,000 per year. All regression analyses were performed in RStudio version 2022.2.3.492 with R version 4.2.0 (2022-04-22 ucrt) [@rcoreteam2022; @rstudioteam2022].
